AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-22 Paper/main.tex
10-22 paper

\begin{figure}[!tpb]%figure4
    \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
    \caption{wait2write}\label{fig:07}
\end{figure}

>>>>

\begin{figure}[!tpb]%figure4
    \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
    \caption{
Performance comparisons for methods before and after integrating with hand-crafted biological features, 
where DeepHF is the RNN integrated with hand-crafted biological features, 
and StAC is the EnAC integrated with hand-crafted biological features. 
The box plot show the mean and distribution of Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests.
}\label{fig:07}
\end{figure}
